---
#############################################################
#   Click on "Knit" in RStudio to render this worksheet.    #
#   Acknowledgements: adapted from Claus O. Wilke           #
#############################################################
title: "Intro to R Markdown"
author: "Write your name here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

Much of the work in this class will be done via R Markdown documents. R Markdown documents are documents that combine text, R code, and R output, including figures. They are a great way to produce self-contained and documented statistical analyses.

In this first worksheet, you will learn how to do some basic markdown editing. After you have made a change to the document, press "Knit HTML" in R Studio and see what kind of a result you get.

Edit below this line.

---------------------------------------------

## 1. Basic Markdown editing

Try out basic R Markdown features, as described here: https://rmarkdown.rstudio.com/authoring_basics.html. Write some text that is bold, and some that is in italics. Make a numbered list and a bulleted list. Make a nested list. Try the block-quote feature.

## 2. Embedding R code

R code embedded in R chunks will be executed and the output will be shown.
```{r}
# R code goes here
x <- rnorm(10)    # random sample from normal distribution
hist(x)           # plot density
```

Try increasing the number of draws from the normal distribution and see what happens.

You can also write inline code. For example: the mean of x is `r mean(x)`.

Now you try:

1. What is the minimum value of x? 

2. What is the maximum value of x?

Note these numbers will change every time you run the file because x is a random sample.

If you want to ensure reproducibility, you could first use the function `set.seed()`:
```{r}
# R code goes here
set.seed(12345)
x <- rnorm(10)    # random sample from normal distribution
mean(x)           # compute x's mean
```
