---
title: "Distributions"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
require(showtext) # optional, but suggested by xaringanthemer functions
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)
```

class: center middle main-title section-title-4

# Distributions

.class-info[

**Week 8**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Fall 2025

Acknowledgements: 
[Andrew Heiss](https://datavizm20.classes.andrewheiss.com), 
[Claus Wilke](https://wilkelab.org/SDS375/)
<!-- [Grant McDermott](https://github.com/uo-ec607/lectures), -->
<!-- [Jenny Bryan](https://stat545.com/join-cheatsheet.html), -->
<!-- [Allison Horst](https://github.com/allisonhorst/stats-illustrations) -->

]

---

# Announcements

Prelim 1 grades are posted on canvas

Questions about your grade? Please:
  1. Meet with Victor first for clarification regarding any grade deductions
  2. If you have further questions, [schedule a meeting with me](https://aem2850.youcanbook.me/)
  3. [Email me](mailto:gerarden@cornell.edu) if the available meeting times do not work for you

Prelim 2 may be more difficult, may be a different format, or both

--

We will provide details on the group project in the next 1-2 weeks

--

Questions before we get started?

---

# Plan for this week

.pull-left[
### Tuesday
  - *Fall Break: No class on Oct 14*
]

.pull-right[
### Thursday
  - [Distributions](#distributions)
  - [example-08-2](#example-2)
]

---

class: inverse, center, middle
name: distributions

# Distributions

```{r, include=FALSE}
theme_xaringan_restore_defaults() # revert to ggplot2 defaults for remainder
theme_set(theme_gray(base_size = 18)) # increase base text size
```

---

# Problems with single numbers
  
.pull-left[

```{r animal-weight-bar, echo=FALSE, fig.dim=c(4.8, 3.75), out.width="100%"}
set.seed(1234)
animals <- tibble(animal = c(rep(c("Small A", "Big A"), each = 250), rep("B", 500))) |> 
  mutate(weight = case_when(
    animal == "Small A" ~ rnorm(n(), 20, 5),
    animal == "Big A" ~ rnorm(n(), 60, 5),
    animal == "B" ~ rnorm(n(), 40, 10)
  )) |> 
  mutate(animal_type = ifelse(str_detect(animal, "A"), "A", "B"))

animals_mean <- animals |> 
  group_by(animal_type) |> 
  summarize(avg_weight = mean(weight))

ggplot(animals_mean, aes(x = animal_type, y = avg_weight, fill = animal_type)) + 
  geom_col() +
  labs(x = "Group", y = "Outcome") +
  ylim(0, 75) +
  guides(fill = "none")
```
  
]

.pull-right[
  
```{r animal-weight-points, echo=FALSE, fig.dim=c(4.8, 3.75), out.width="100%"}
ggplot(animals, aes(x = animal_type, y = weight, color = animal_type)) +
  geom_point(position = position_jitter(height = 0), size = 1) +
  stat_summary(geom = "point", fun = "mean", size = 5, color = "darkred") +
  labs(x = "Group", y = "Outcome") +
  guides(color = "none")
```
]

---
  
# More information is (almost) always better
  
**Avoid visualizing single numbers when you have a whole range or distribution of numbers**

--
  
Uncertainty in single variables

Uncertainty across multiple variables

Uncertainty in models and simulations

--

**What are some common methods for visualizing distributions?**

--

Histograms, densities, box plots, etc.

---

# Histograms

What are they?

--

Put data into equally spaced buckets (or "bins") based on values of a variable, plot how many rows of the data frame are in each bucket

---
  
# Histograms

How would we use the grammar of graphics to make a histogram of `lifeExp`?

```{r basic-histogram-data, eval=FALSE}
library(gapminder)

gapminder_2002 <- gapminder |> 
  filter(year == 2002)

head(gapminder_2002)
```

```{r basic-histogram-data-mask, echo=FALSE}
library(gapminder)

gapminder_2002 <- gapminder |> 
  filter(year == 2002) |> 
  mutate(continent = case_match(continent,
                                "Oceania" ~ as_factor("Asia"),
                                .default = continent))

head(gapminder_2002)
```

---
  
# Histograms

.left-code[
```{r basic-histogram, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 3.5), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) + #<<
  geom_histogram() #<<
```
]

.right-plot[
  ![](`r knitr::fig_chunk("basic-histogram", "png")`)
]


---
  
# Histograms: binwidth argument
  
No official rule for what makes a good bin width

.pull-left-3[
.center.small[Too narrow:]

.center.tiny[`geom_histogram(binwidth = .2)`]

```{r hist-too-narrow, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_histogram(binwidth = 0.2)
```
  
]

--
  
.pull-middle-3[
.center.small[Too wide:]

.center.tiny[`geom_histogram(binwidth = 50)`]

```{r hist-too-wide, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_histogram(binwidth = 50)
```
]

--
  
.pull-right-3[
.center.small[(One type of) just right:]

.center.tiny[`geom_histogram(binwidth = 5)`]
  
```{r hist-just-right, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_histogram(binwidth = 5)
```
]

---
  
# Histograms: tips using other arguments

.pull-left[
.center[Add a border to the bars<br>for readability]

.center.tiny[`geom_histogram(..., color = "white")`]
    
```{r hist-border, echo=FALSE, fig.dim=c(4.5, 3), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white")
```
]

--
  
.pull-right[
.center.small[Set the boundary;<br>bucket now 50–55, not 47.5–52.5]

.center.tiny[`geom_histogram(..., boundary = 50)`]

```{r hist-boundary, echo=FALSE, fig.dim=c(4.5, 3), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_histogram(binwidth = 5, color = "white", boundary = 50)
```

]

---
  
# Density plots
  
What are they?

--

Estimates of the **probability *density* function** of a random variable

--

Histograms show raw counts; density plots show proportions (integrate to 1)

--

How would we use the grammar of graphics to make a density plot of `lifeExp`?

---
  
# Density plots
  
.left-code[
```{r basic-density, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 3.5), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) + 
  geom_density() #<<
```
]

.right-plot[
  ![](`r knitr::fig_chunk("basic-density", "png")`)
]

---
  
# Density plots: add some color
  
.left-code[
```{r basic-density-color, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 3.5), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue") #<<
```

We can use aesthetics as parameters inside a geom rather than inside an **aes()** statement

Here we used **fill = "skyblue"**
]

.right-plot[
  ![](`r knitr::fig_chunk("basic-density-color", "png")`)
]

---
  
# Density plots: bandwidths

Different options for calculus change the plot shape

.pull-left-3[
.center.small[`bw = 1`]

```{r gaussian-bw-1, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "gaussian", bw = 1)
```
  
]

--
  
.pull-middle-3[
.center.small[`bw = 10`]

```{r gaussian-bw-10, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "gaussian", bw = 10)
```
]

--
  
.pull-right-3[
.center.small[`bw = "nrd0"` <small>(default)</small>]
    
```{r gaussian-bw-auto, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "gaussian")
```
]

---
  
# Density plots: kernels
  
Different options for calculus change the plot shape

.pull-left-3[
.center.small[`kernel = "gaussian"`]

```{r gaussian-kernel-gaussian, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "gaussian")
```
  
]

.pull-middle-3[
.center.small[`"epanechnikov"`]

```{r gaussian-kernel-epanechnikov, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "epanechnikov")
```
]

.pull-right-3[
.center.small[`"rectangular"`]

```{r gaussian-kernel-rectangular, echo=FALSE, fig.dim=c(4.5, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_density(fill = "skyblue",
               kernel = "rectangular")
```
]

---
  
# Box and whisker plots

What are they?

--

Graphical representations of specific points in a distribution


---
  
# Box and whisker plots
  
```{r boxplot-explanation, echo=FALSE, fig.width=8, fig.height=3.5, out.width="100%"}
hwy_50 <- quantile(mpg$hwy, 0.5)
hwy_25 <- quantile(mpg$hwy, 0.25)
hwy_75 <- quantile(mpg$hwy, 0.75)
hwy_iqr <- hwy_75 - hwy_25

# Technically this should just be hwy_75 + 1.5 * IQR, but ggplot does odd things
# with small datasets
hwy_min <- boxplot.stats(mpg$hwy)$stats[1]
hwy_max <- boxplot.stats(mpg$hwy)$stats[5]

hwy_out <- boxplot.stats(mpg$hwy)$out

mpg |> 
  ggplot(aes(x = hwy)) +
  geom_boxplot(fill = "#F7F7F7", color = "#B31B1B") +
  annotate(geom = "text", x = hwy_50, y = 0.48, label = "Median", fontface = "bold") +
  annotate(geom = "segment", x = hwy_50, xend = hwy_50, y = 0.44, yend = 0.4,
           arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "text", x = hwy_25, y = 0.48, label = "25%", fontface = "bold") +
  annotate(geom = "segment", x = hwy_25, xend = hwy_25, y = 0.44, yend = 0.4,
           arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "text", x = hwy_75, y = 0.48, label = "75%", fontface = "bold") +
  annotate(geom = "segment", x = hwy_75, xend = hwy_75, y = 0.44, yend = 0.4,
           arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "text", x = hwy_25 + 0.5 * hwy_iqr, y = -0.52, 
           label = "Interquartile range (IQR)", fontface = "bold") +
  annotate(geom = "segment", x = c(hwy_25, hwy_75), xend = c(hwy_25, hwy_75), 
           y = -0.46, yend = -0.4, arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "segment", x = hwy_25, xend = hwy_75, y = -0.46, yend = -0.46) +
  annotate(geom = "text", x = hwy_min, y = 0.15, label = "Minimum\n25% − (1.5 × IQR)",
           hjust = 0, lineheight = 1, fontface = "bold") +
  annotate(geom = "segment", x = hwy_min, xend = hwy_min, y = 0.06, yend = 0.02,
           arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "text", x = hwy_max, y = 0.15, label = "Maximum\n75% + (1.5 × IQR)",
           hjust = 1, lineheight = 1, fontface = "bold") +
  annotate(geom = "segment", x = hwy_max, xend = hwy_max, y = 0.06, yend = 0.02,
           arrow = arrow(length = unit(0.3, "lines")))  +
  annotate(geom = "text", x = min(hwy_out) + 0.5 * (max(hwy_out) - min(hwy_out)), y = -0.16, 
           label = "Outliers", fontface = "bold") +
  annotate(geom = "segment", x = c(min(hwy_out), max(hwy_out)), xend = c(min(hwy_out), max(hwy_out)), 
           y = -0.1, yend = -0.04, arrow = arrow(length = unit(0.3, "lines"))) +
  annotate(geom = "segment", x = min(hwy_out), xend = max(hwy_out),
           y = -0.1, yend = -0.1) +
  labs(x = "Highway MPG") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

---
  
# Box and whisker plots

What are they?

Graphical representations of specific points in a distribution

How could we use ggplot to make a boxplot of `lifeExp`?

---
  
# Box and whisker plots

.left-code[
```{r basic-boxplot, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 2.75), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) + 
  geom_boxplot() #<<
```

What do the y axis numbers mean?
]

.right-plot[
  ![](`r knitr::fig_chunk("basic-boxplot", "png")`)
]

---
  
# Box and whisker plots

Use `theme()` to customize the plot for this geom

.left-code[
```{r basic-boxplot-no-y, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 2.75), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp)) +
  geom_boxplot() +
  theme( #<<
    axis.text.y = element_blank(), #<<
    axis.ticks.y = element_blank(), #<<
    panel.grid.major.y = element_blank(), #<<
    panel.grid.minor.y = element_blank() #<<
  ) #<<
```

]

.right-plot[
  ![](`r knitr::fig_chunk("basic-boxplot-no-y", "png")`)
]


---
  
# Uncertainty across multiple variables
  
```{r, include=FALSE}
theme_set(theme_gray(base_size = 16)) # decrease base text size
```

How could we visualize the distribution of a single variable across groups?

--

Add a `fill` aesthetic or use facets!

---
  
# Multiple histograms
  
Fill with a different variable

.left-code[
```{r histogram-fill, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 3.5), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp,
             fill = continent)) + #<<
  geom_histogram(binwidth = 5, 
                 color = "white", 
                 boundary = 50) +
  theme(legend.position = "bottom") +
  labs(fill = NULL)
```

This stacked histogram is bad and hard to read though
]

.right-plot[
  ![](`r knitr::fig_chunk("histogram-fill", "png")`)
]

---
  
# Multiple histograms
  
Facet with a different variable

.left-code[
```{r histogram-facet, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 3.5), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp,
             fill = continent)) +
  geom_histogram(binwidth = 5, 
                 color = "white", 
                 boundary = 50) +
  facet_wrap(vars(continent)) + #<<
  guides(fill = "none") #<<
```
]

.right-plot[
  ![](`r knitr::fig_chunk("histogram-facet", "png")`)
]

---

# Multiple densities: Transparency

.left-code[
```{r density-fill, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(x = lifeExp,
             fill = continent)) +
  geom_density(alpha = 0.5) + #<<
  theme(legend.position = "bottom") +
  labs(fill = NULL)
```

But be careful, these can get confusing quickly

With many groups, better to space them out using ridgeline plots
]

.right-plot[
![](`r knitr::fig_chunk("density-fill", "png")`)
]

---

# Multiple densities: Ridgeline plots

.left-code[
```{r density-ridges, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 4.2), out.width="100%"}
library(ggridges) #<<

gapminder_2002 |> 
  ggplot(aes(x = lifeExp,
             fill = continent,
             y = continent)) + #<<
  guides(fill = "none") +
  labs(y = NULL) +
  geom_density_ridges() #<<
```

There is no explicit scale for the densities anymore (it is shared with y)

With many densities, use a single fill color to prevent distraction
]

.right-plot[
![](`r knitr::fig_chunk("density-ridges", "png")`)
]


---

# Multiple box and whisker plots

.left-code[
```{r multiple-boxplots, tidy=FALSE, message=FALSE, fig.show="hide", fig.dim=c(4.8, 4.2), out.width="100%"}
gapminder_2002 |> 
  ggplot(aes(
    x = lifeExp,
    fill = continent,
    y = continent
  )) + 
  guides(fill = "none") +
  labs(y = NULL) +
  geom_boxplot() #<<
```
]

.right-plot[
![](`r knitr::fig_chunk("multiple-boxplots", "png")`)
]


---
class: inverse, center, middle
name: example-2

# example-08-2:<br>distributions-practice.R
