---
class: inverse, center, middle
name: prologue

# Prologue

```{r read-survey-responses, include=FALSE}
# load data
# survey <- read_csv("data/survey-responses-midsemester/survey_responses.csv")
# summary_questions <- survey |>
#   select(id, contains(":"))
# names(summary_questions) <- str_replace( names(summary_questions), ".*: ", "")

# make a function for plotting responses
```

---

# Thank you!

I read all the Reflection - Week 6 survey responses

I will briefly summarize some of the responses and share some reactions

Please don't hesitate to provide feedback on how the course progresses!

---

# Please rate the pace overall:

```{r, echo=FALSE}
# summary_questions |>
#   ggplot(aes(x = fct_relevel(`Please rate the pace overall:`,
#                                 "too slow", "about right", "too fast")
#                                 )) +
#   geom_bar() +
#   labs(x = NULL,
#        y = "number of students") +
#   theme_xaringan()
```


---

# Please rate the difficulty overall:

```{r, echo=FALSE}
# summary_questions |>
#   ggplot(aes(x = fct_relevel(`Please rate the difficulty overall:`,
#                                 "too easy", "about right", "too difficult")
#                                 )) +
#   geom_bar() +
#   labs(x = NULL,
#        y = "number of students") +
#   theme_xaringan()
```


---

# Please rate the workload overall:

```{r, echo=FALSE}
# summary_questions |>
#   group_by(`Please rate the workload overall:`) |> count() |> ungroup() |>
#   add_row(`Please rate the workload overall:` = "too little", n = 0) |>
#   ggplot(aes(x = fct_relevel(`Please rate the workload overall:`,
#                                 "too little", "about right", "too much"),
#              y = n)) +
#   geom_col() +
#   labs(x = NULL,
#        y = "number of students") +
#   theme_xaringan()
```


---

# RStudio Cloud versus a local install?

```{r, echo=FALSE}
# summary_questions |>
#   rename(preference = contains("preference")) |>
#   ggplot(aes(x = preference)) +
#   geom_bar() +
#   labs(x = NULL,
#        y = "number of students") +
#   theme_xaringan()
```


---

# Some themes:

**Desire for more business applications**
- We will work on this, especially on projects

--

**Several people requested guidance on installing/working locally**
- I will post some basic guidance on the course site
- Come to office hours if you want help installing R+RStudio!

--

**Examples: make them more open-ended/challenging + work more as a group**
- I will experiment with this!

--

**Interest in modeling, statistical methods, linear regression, etc.**

