---

# Plan for today

[Group project](#group-project)

---
class: inverse, center, middle
name: group-project

# Group project

---

# Group project

Use R and the tidyverse to wrangle and visualize equities data

#### Multiple parts:
1. AAPL
2. The S&P 500
3. Our Class Portfolio
4. Something extra for 5850 students (TBD)

```{r load-project-data, include=FALSE}
load("../../rstudio-cloud/group-project/sp500.RData")
our_companies <- read_csv("../../rstudio-cloud/group-project/our-companies.csv")
```

---

# Group project: data

```{r}
sp500_companies
```

---

# Group project: data

```{r}
sp500_prices
```

---

# Group project: data

```{r}
our_companies
```

---

# Group project: overview

First: you choose groups of 3
  - All group members must be in the same section (i.e., 2850 or 5850)

Write quarto report that summarizes your work, presents visualizations, and discusses takeaways

Do not use any packages outside base R and the tidyverse

Limited TA help for Part 3!

Due: Friday, April 12 at 11:59pm (after spring break)

