---
title: "Functions and iteration"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)

load("data/12-slides/sp500.RData")
```


class: center, middle

# Functions and iteration

.class-info[

**Week 12**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Spring 2025

Acknowledgements: 
<!-- [Andrew Heiss](https://datavizm20.classes.andrewheiss.com) -->
[Claus Wilke](https://wilkelab.org/SDS375/)
<!-- [Grant McDermott](https://github.com/uo-ec607/lectures) -->
<!-- [Jenny Bryan](https://stat545.com/join-cheatsheet.html), -->
<!-- [Allison Horst](https://github.com/allisonhorst/stats-illustrations) -->

]

---

# Announcements

**Group project due this Friday, April 18!**

Office hours for the rest of this week:
  - Tuesday: Prof. Gerarden open office hours from 11:30-12:30 in Warren 464
  - Tuesday: Prof. Gerarden by appointment at [aem2850.youcanbook.me](https://aem2850.youcanbook.me)
  - Thursday: Prof. Gerarden by appointment (already fully booked)
  - Friday: extra TA office hours from 2:00-4:00 in Warren 175

We will have a regular homework this week (due Monday 4/21)
  - We will have regular TA office hours on Monday

Questions before we get started?

---

# Plan for this week

.pull-left[
### Tuesday
  - [Intro to functions and iteration](#functions-intro)
  - [example-12-1](#example-1)
]

.pull-right[
### Thursday
  - [Conditional execution](#conditional-execution)
  - [Functions with multiple arguments](#multiple-arguments)
  - [example-12-2](#example-2)
]

---
class: inverse, center, middle
name: functions-intro

# Intro to functions and iteration

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-aapl, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
What needs to change if we want to look at AMZN share prices instead?
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-amzn, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "AMZN") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AMZN") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-amzn", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-tsla, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "TSLA") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: TSLA") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla", "png")`)
]

---

# How can we avoid duplication and mistakes?

--

1. **Avoid hard-coding specific values**

2. **Define a function**

3. **Automate calling the function**

4. Write a more general function

5. Use these concepts in a tidy pipeline

We will focus on steps 1-3 due to time constraints

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-aapl1a, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```

What is "hard-coded" here?
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-aapl1b, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```

How can we avoid this hard-coding?
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-aapl2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "AAPL" #<<

sp500_prices |> 
  filter(symbol == ticker) |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
**str_glue()** allows us to put the contents of **ticker** in the plot's title
]

--

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-amzn2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "AMZN" #<<

sp500_prices |> 
  filter(symbol == ticker) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **ticker** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-amzn2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-tsla2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "TSLA" #<<

sp500_prices |> 
  filter(symbol == ticker) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **ticker** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla2", "png")`)
]


---

# Step 2: Define a function

--

.left-code[
```{r eval = FALSE}
make_plot <- function(ticker) { #<<
  sp500_prices |> 
    filter(symbol == ticker) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = str_glue("Symbol: {ticker}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
} #<<
```
]

.pull-right[
Three key steps:
1. Pick a **name**
2. List **arguments** inside `function()`
3. Put code in the **body** of the function, delimited by `{...}`

Easiest to write the body on a test case, *then* convert it into a function
]

---

# Step 2: Define a function

.left-code[
```{r stock-plot-aapl3, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
make_plot <- function(ticker) {
  sp500_prices |> 
    filter(symbol == ticker) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = str_glue("Symbol: {ticker}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
}

make_plot("AAPL") #<<
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl3", "png")`)
]

---

# Step 2: Define a function

.pull-left[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("AMZN") #<<
```
]

.pull-right[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("TSLA") #<<
```
]


---

# Rules of thumb about functions

--

- You can (almost) never write too many functions

--

- When you find yourself writing the same code 3+ times, put it into a function

--

- A function should be no longer than 20-40 lines

--

- If a function is getting too long, break it into smaller functions


---

# Step 3: Automate calling the function

Individual function calls are hard to scale

```{r, eval=FALSE}
make_plot("AAPL")
make_plot("AMZN")
make_plot("TSLA")
```

What if we wanted to make this plot for every company in the S&P 500?

How could you automate these function calls?

--

1. Imperative programming (for loops)

2. Functional programming (map functions)

---

# Step 3: Automate calling the function

The `purrr` packages provides `map` functions that take a vector as input, apply a **function** to each element of the vector, and return the results in a new vector:

```{r, eval = FALSE}
map(some_vector, some_function)
```

- `map` functions are basically identical to base R's `apply` functions

--

**How can we use map to make plots for AAPL, AMZN, and TSLA?**

--

```{r}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- map(symbols, make_plot)
```

--

Here `map` takes each element of the vector `symbols` and uses it as input for our function `make_plot()`

---

# Step 3: Automate calling the function

`map` returns a **list**. In this example, it's a list of plots that we assigned to `plots`:

.small-code[
```{r}
class(plots)
```
]

--

.pull-left-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[1]]
```
]

--

.pull-middle-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[2]]
```
]

--

.pull-right-3.small-code[
The syntax `plots[[x]]` allows us to drill down into the list `plots` and extract whatever object is in the `x`th position (here: a ggplot)
]

---

# Step 3: Automate calling the function

This scales really easily!

.small-code[
```{r all-symbols}
all_symbols <- sp500_prices |> distinct(symbol) |> pull() # get all the symbols in the S&P 500 #<<
all_plots <- map(all_symbols, make_plot) # make a plot for each of the symbols
```
]

--

.pull-left-3[
```{r length-all-symbols}
length(all_symbols)
length(all_plots)
```
]

--

.pull-middle-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[35]]
```
]

--

.pull-right-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[500]]
```
]

---

# Step 3: Automate calling the function

We can also extract results using logical expressions:

```{r failed-bank-code, fig.dim=c(4, 3), out.width="45%", eval = FALSE}
all_plots[all_symbols=="FRCB"]
```

```{r failed-bank-output, fig.dim=c(4, 3), out.width="45%", echo = FALSE}
all_plots[all_symbols=="FRCB"][[1]] # extract plot from list
```

---

# The map functions

The `purrr` package provides a family of `map` functions that return different types of output:

- `map()` makes a list
- `map_lgl()` makes a logical vector
- `map_int()` makes an integer vector
- `map_dbl()` makes a double vector
- `map_chr()` makes a character vector

---

# What about `for` loops?

For loops work too!

```{r, eval=FALSE}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- vector("list", length(symbols)) # 1. allocate space for output
for (i in seq_along(symbols)) {          # 2. specify the sequence to loop over
  plots[[i]] <- make_plot(symbols[i])    # 3. specify what to do in each iteration
}
```

--

But functional programming is more concise:
```{r, eval=FALSE}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- map(symbols, make_plot)
```

---

# Why not use `for` loops?

--

- They often require us to think about data logistics (indexing)

--

- They encourage iterative thinking over conceptual thinking

--

- Typically require more code, which often means more errors

--

- Can be harder to parallelize or otherwise optimize

--

**But there is nothing wrong with using them!**

We can practice using `for` loops during the example if time permits

---
class: inverse, center, middle
name: example-1

# example-12-1

---
class: inverse, center, middle
name: conditional-execution

# Conditional execution


---
class: inverse, center, middle
name: multiple-arguments

# Functions with multiple arguments



---
class: inverse, center, middle
name: example-2

# example-12-2

