---
title: "Functions and iteration"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)

load("data/sp500.RData")
```


class: center, middle

# Functions and iteration

.class-info[

**Week 14**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Spring 2023

Acknowledgements: 
<!-- [Andrew Heiss](https://datavizm20.classes.andrewheiss.com) -->
[Claus Wilke](https://wilkelab.org/SDS375/)
<!-- [Grant McDermott](https://github.com/uo-ec607/lectures) -->
<!-- [Jenny Bryan](https://stat545.com/join-cheatsheet.html), -->
<!-- [Allison Horst](https://github.com/allisonhorst/stats-illustrations) -->

]

---

# Announcements



Questions before we get started?


---

# Plan for today

<!-- [Prologue](#prologue) -->

[Course evaluations](#course-evals)

[Functions and iteration](#functions)

[Example 12](#example)

---
class: inverse, center, middle
name: course-evals

# Course evaluations

---

# Course evaluations

I take feedback seriously and will use it to improve this course!

Extra useful since this is the first offering of AEM 2850

--

Concrete suggestions are most helpful

--

**I would appreciate your feedback through two channels:**

1. Reflection - Week 15 - Course Feedback Survey
2. University course evaluations

--

Both will be anonymous

---

# University course evaluations

Anonymous: we just get summary reports, after grades are submitted

**I will award a bonus point on Lab 15 for completing evaluations**

Thank you in advance for your feedback!

---
class: inverse, center, middle
name: functions

# Functions and iteration

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-aapl, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

--

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-nvda, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "NVDA") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: NVDA") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-nvda", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-tsla, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "TSLA") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: TSLA") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla", "png")`)
]

---

# How can we avoid duplication and mistakes?

--

1. Avoid hard-coding specific values

2. Define a function

3. Automate calling the function

4. Write a more general function

5. Use these concepts in a tidy pipeline

--

We will focus on steps 1-3 due to time constraints

---

# Step 1: Avoid hard-coding specific values

What is "hard-coded" here?

.left-code[
```{r stock-plot-aapl1a, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

---

# Step 1: Avoid hard-coding specific values

How can we avoid this hard-coding?

.left-code[
```{r stock-plot-aapl1b, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-aapl2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
library(glue) # evaluate R code inside strings
symbol_choice <- "AAPL" #<<

sp500_prices |> 
  filter(symbol == symbol_choice) |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = glue("Symbol: {symbol_choice}")) + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
**glue()** allows us to put the contents of **symbol_choice** in the plot's title
]

--

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-nvda2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
library(glue) # evaluate R code inside strings
symbol_choice <- "NVDA" #<<

sp500_prices |> 
  filter(symbol == symbol_choice) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = glue("Symbol: {symbol_choice}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **symbol_choice** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-nvda2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-tsla2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
library(glue) # evaluate R code inside strings
symbol_choice <- "TSLA" #<<

sp500_prices |> 
  filter(symbol == symbol_choice) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = glue("Symbol: {symbol_choice}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **symbol_choice** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla2", "png")`)
]


---

# Step 2: Define a function

--

.left-code[
```{r eval = FALSE}
make_plot <- function(symbol_choice) { #<<
  sp500_prices |> 
    filter(symbol == symbol_choice) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = glue("Symbol: {symbol_choice}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
} #<<
```
]

.pull-right[
Three key steps:
1. Pick a **name**
2. List **arguments** inside `function()`
3. Put code in the **body** of the function, delimited by `{...}`

Easiest to write the body on a test case, *then* convert it into a function
]

---

# Step 2: Define a function

.left-code[
```{r stock-plot-aapl3, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
make_plot <- function(symbol_choice) {
  sp500_prices |> 
    filter(symbol == symbol_choice) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = glue("Symbol: {symbol_choice}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
}

make_plot("AAPL") #<<
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl3", "png")`)
]

---

# Step 2: Define a function

.pull-left[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("NVDA") #<<
```
]

.pull-right[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("TSLA") #<<
```
]


---

# Rules of thumb about functions

--

- You can never write too many functions

--

- When you find yourself writing the same code 2-3 times, put it into a function

--

- A function should be no longer than 20-40 lines

--

- If a function is getting too long, break it into smaller functions


---

# Step 3: Automate calling the function

Individual function calls are hard to scale

```{r, eval=FALSE}
make_plot("AAPL")
make_plot("NVDA")
make_plot("TSLA")
```

What if we wanted to make this plot for every company in the S&P 500?

How could you automate these function calls?

--

1. Imperative programming (for loops)

2. Functional programming (map functions)

---

# Step 3: Automate calling the function

The `purrr` packages provides `map` functions that take a vector as input, apply a **function** to each element of the vector, and return the results in a new vector:

```{r, eval = FALSE}
map(some_vector, some_function)
```

- `map` functions are basically identical to base R's `apply` functions

--

**How can we use map to make plots for AAPL, NVDA, and TSLA?**

--

```{r}
symbols <- c("AAPL", "NVDA", "TSLA")
plots <- map(symbols, make_plot)
```

--

Here `map` takes each element of the vector `symbols` and uses it as input for our function `make_plot()`

---

# Step 3: Automate calling the function

`map` returns a **list**. In this example, it's a list of plots that we assigned to `plots`:

.small-code[
```{r}
class(plots)
```
]

--

.pull-left-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[1]]
```
]

--

.pull-middle-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[2]]
```
]

--

.pull-right-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[3]]
```
]

---

# Step 3: Automate calling the function

This scales really easily!

.small-code[
```{r}
all_symbols <- sp500_prices |> distinct(symbol) |> pull() # get all the symbols in the S&P 500 #<<
all_plots <- map(all_symbols, make_plot) # make a plot for each of the symbols
```
]

--

.pull-left-3[
```{r, warnings = FALSE}
length(all_symbols)
length(all_plots)
```
]

--

.pull-middle-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[279]]
```
]

--

.pull-right-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[504]]
```
]

---

# The map functions

The `purrr` package provides a family of `map` functions that return different types of output:

- `map()` makes a list
- `map_lgl()` makes a logical vector
- `map_int()` makes an integer vector
- `map_dbl()` makes a double vector
- `map_chr()` makes a character vector

---

# What about `for` loops?

For loops work too!

```{r, eval=FALSE}
symbols <- c("AAPL", "NVDA", "TSLA")
plots <- vector("list", length(symbols)) # 1. allocate space for output
for (i in seq_along(symbols)) {          # 2. specify the sequence to loop over
  plots[[i]] <- make_plot(symbols[i])    # 3. specify what to do in each iteration
}
```

--

But functional programming is more concise:
```{r, eval=FALSE}
symbols <- c("AAPL", "NVDA", "TSLA")
plots <- map(symbols, make_plot)
```

---

# Why not use `for` loops?

--

- They often require us to think about data logistics (indexing)

--

- They encourage iterative thinking over conceptual thinking

--

- Typically require more code, which often means more errors

--

- Harder to parallelize or otherwise optimize

--

**But there is nothing wrong with using them!**


---
class: inverse, center, middle
name: example

# Example 12

