---
title: "Functions and iteration"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)

load("data/sp500.RData")
```


class: center, middle

# Functions and iteration

.class-info[

**Week 14**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Spring 2024

Acknowledgements: 
<!-- [Andrew Heiss](https://datavizm20.classes.andrewheiss.com) -->
[Claus Wilke](https://wilkelab.org/SDS375/)
<!-- [Grant McDermott](https://github.com/uo-ec607/lectures) -->
<!-- [Jenny Bryan](https://stat545.com/join-cheatsheet.html), -->
<!-- [Allison Horst](https://github.com/allisonhorst/stats-illustrations) -->

]

---

# Announcements

Plan for this week:
  - Today: slides and a short example
  - Thursday: course evaluations, prelim 2 Q&A, **Lab-14**
    - If you come to class and work through the lab you should get full credit
    - Due Thursday at 11:59pm so you can focus on studying for prelim 2

--

Plan for next week:
  - **Prelim 2** in class on Tuesday, May 9 at 9:40am
  - **Lab 15 - Course Survey** due Monday, May 15 at 11:59pm

--

Questions before we get started?

---

# Plan for today

<!-- [Prologue](#prologue) -->

[Course evaluations](#course-evals)

[Functions and iteration](#functions)

[example-14](#example)

---
class: inverse, center, middle
name: course-evals

# Course evaluations

---

# Course objectives reminder

1. Develop basic proficiency in `R` programming
2. Understand data structures and manipulation
3. Describe effective techniques for data visualization and communication
4. Construct effective data visualizations
5. Utilize course concepts and tools for business applications

With these objectives in mind...

---

# Please complete course evaluations

I take feedback seriously and will use it to improve this course!

Extra useful since this is only the second offering of AEM 2850 / 5850

--

Concrete suggestions are most helpful

--

**I would appreciate your feedback through two channels:**

1. Lab 15 - Course Feedback Survey (on canvas)
2. University course evaluations

--

Both will be anonymous

**I will give you time to complete these in class on Thursday**

---

# Lab 15 - course feedback survey

Anonymous: canvas reports whether you submit but does not link responses to individuals

Survey is very short, should only take 5 minutes!

I will give you time in class Thursday to complete it

---

# University course evaluations

Anonymous: we just get summary reports, after grades are submitted

**I will award a bonus point on Lab 15 for completing evaluations**

I will give you time in class Thursday to complete it

Thank you in advance for your feedback!

---
class: inverse, center, middle
name: functions

# Functions and iteration

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-aapl, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
What needs to change if we want to look at AMZN share prices instead?
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-amzn, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "AMZN") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AMZN") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-amzn", "png")`)
]

---

# We often run similar code multiple times

.left-code[
```{r stock-plot-tsla, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
sp500_prices |> 
  filter(symbol == "TSLA") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: TSLA") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla", "png")`)
]

---

# How can we avoid duplication and mistakes?

--

1. **Avoid hard-coding specific values**

2. **Define a function**

3. **Automate calling the function**

4. Write a more general function

5. Use these concepts in a tidy pipeline

We will focus on steps 1-3 due to time constraints

---

# Step 1: Avoid hard-coding specific values

What is "hard-coded" here?

.left-code[
```{r stock-plot-aapl1a, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> 
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

---

# Step 1: Avoid hard-coding specific values

How can we avoid this hard-coding?

.left-code[
```{r stock-plot-aapl1b, eval=FALSE}
sp500_prices |> 
  filter(symbol == "AAPL") |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = "Symbol: AAPL") + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-aapl2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "AAPL" #<<

sp500_prices |> 
  filter(symbol == ticker) |> #<<
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) + #<<
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
**str_glue()** allows us to put the contents of **ticker** in the plot's title
]

--

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-amzn2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "AMZN" #<<

sp500_prices |> 
  filter(symbol == ticker) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **ticker** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-amzn2", "png")`)
]

---

# Step 1: Avoid hard-coding specific values

.left-code[
```{r stock-plot-tsla2, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
ticker <- "TSLA" #<<

sp500_prices |> 
  filter(symbol == ticker) |>
  ggplot(aes(x = date, y = adjusted)) +
  geom_line() +
  labs(x = NULL,
       y = "Share price ($)",
       title = str_glue("Symbol: {ticker}")) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") +
  scale_y_continuous(limits = c(0, NA)) +
  theme_bw()
```
Now **ticker** is the only thing that changes
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-tsla2", "png")`)
]


---

# Step 2: Define a function

--

.left-code[
```{r eval = FALSE}
make_plot <- function(ticker) { #<<
  sp500_prices |> 
    filter(symbol == ticker) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = str_glue("Symbol: {ticker}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
} #<<
```
]

.pull-right[
Three key steps:
1. Pick a **name**
2. List **arguments** inside `function()`
3. Put code in the **body** of the function, delimited by `{...}`

Easiest to write the body on a test case, *then* convert it into a function
]

---

# Step 2: Define a function

.left-code[
```{r stock-plot-aapl3, fig.show="hide", fig.dim=c(4, 3), out.width="100%"}
make_plot <- function(ticker) {
  sp500_prices |> 
    filter(symbol == ticker) |>
    ggplot(aes(x = date, y = adjusted)) +
    geom_line() +
    labs(x = NULL,
         y = "Share price ($)",
         title = str_glue("Symbol: {ticker}")) +
    scale_x_date(date_breaks = "1 year",
                 date_labels = "%Y") +
    scale_y_continuous(limits = c(0, NA)) +
    theme_bw()
}

make_plot("AAPL") #<<
```
]

.right-plot[
![](`r knitr::fig_chunk("stock-plot-aapl3", "png")`)
]

---

# Step 2: Define a function

.pull-left[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("AMZN") #<<
```
]

.pull-right[
```{r fig.dim=c(4, 3), out.width="100%"}
make_plot("TSLA") #<<
```
]


---

# Rules of thumb about functions

--

- You can never write too many functions

--

- When you find yourself writing the same code 2-3 times, put it into a function

--

- A function should be no longer than 20-40 lines

--

- If a function is getting too long, break it into smaller functions


---

# Step 3: Automate calling the function

Individual function calls are hard to scale

```{r, eval=FALSE}
make_plot("AAPL")
make_plot("AMZN")
make_plot("TSLA")
```

What if we wanted to make this plot for every company in the S&P 500?

How could you automate these function calls?

--

1. Imperative programming (for loops)

2. Functional programming (map functions)

---

# Step 3: Automate calling the function

The `purrr` packages provides `map` functions that take a vector as input, apply a **function** to each element of the vector, and return the results in a new vector:

```{r, eval = FALSE}
map(some_vector, some_function)
```

- `map` functions are basically identical to base R's `apply` functions

--

**How can we use map to make plots for AAPL, AMZN, and TSLA?**

--

```{r}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- map(symbols, make_plot)
```

--

Here `map` takes each element of the vector `symbols` and uses it as input for our function `make_plot()`

---

# Step 3: Automate calling the function

`map` returns a **list**. In this example, it's a list of plots that we assigned to `plots`:

.small-code[
```{r}
class(plots)
```
]

--

.pull-left-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[1]]
```
]

--

.pull-middle-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[2]]
```
]

--

.pull-right-3.small-code[
```{r fig.dim=c(4, 3), out.width="100%"}
plots[[3]]
```
]

---

# Step 3: Automate calling the function

This scales really easily!

.small-code[
```{r all-symbols}
all_symbols <- sp500_prices |> distinct(symbol) |> pull() # get all the symbols in the S&P 500 #<<
all_plots <- map(all_symbols, make_plot) # make a plot for each of the symbols
```
]

--

.pull-left-3[
```{r length-all-symbols}
length(all_symbols)
length(all_plots)
```
]

--

.pull-middle-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[33]]
```
]

--

.pull-right-3[
```{r fig.dim=c(4, 3), out.width="100%"}
all_plots[[498]]
```
]

---

# Step 3: Automate calling the function

We can also extract results using logical expressions:

.pull-left-3[
```{r failed-bank-1, fig.dim=c(4, 3), out.width="100%"}
all_plots[all_symbols=="SIVB"]
```
]

.pull-middle-3[
```{r failed-bank-2, fig.dim=c(4, 3), out.width="100%"}
all_plots[all_symbols=="SBNY"]
```
]

.pull-right-3[
```{r failed-bank-3, fig.dim=c(4, 3), out.width="100%"}
all_plots[all_symbols=="FRC"]
```

]

.small[Note: these prices don't reflect the banks' failures since they end in 2022]

---

# The map functions

The `purrr` package provides a family of `map` functions that return different types of output:

- `map()` makes a list
- `map_lgl()` makes a logical vector
- `map_int()` makes an integer vector
- `map_dbl()` makes a double vector
- `map_chr()` makes a character vector

---

# What about `for` loops?

For loops work too!

```{r, eval=FALSE}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- vector("list", length(symbols)) # 1. allocate space for output
for (i in seq_along(symbols)) {          # 2. specify the sequence to loop over
  plots[[i]] <- make_plot(symbols[i])    # 3. specify what to do in each iteration
}
```

--

But functional programming is more concise:
```{r, eval=FALSE}
symbols <- c("AAPL", "AMZN", "TSLA")
plots <- map(symbols, make_plot)
```

---

# Why not use `for` loops?

--

- They often require us to think about data logistics (indexing)

--

- They encourage iterative thinking over conceptual thinking

--

- Typically require more code, which often means more errors

--

- Can be harder to parallelize or otherwise optimize

--

**But there is nothing wrong with using them!**

---
class: inverse, center, middle
name: example

# example-14


---

# Plan for today

<!-- [Prologue](#prologue) -->

[Course evaluations](#course-evals-in-class)

[Prelim 2 info](#prelim-2)

[lab-14](#lab)

---
name: course-evals-in-class

# Please take 10 mins to complete course evals

I take feedback seriously and will use it to improve this course!

Concrete suggestions are most helpful

**I would appreciate your feedback through two channels:**

1. Lab 15 - Course Feedback Survey (on canvas through May 19)
2. University course evaluations (open through May 12)

Both will be anonymous

Reminder: **bonus point on Lab 15 for completing university evaluations**

*Note: if you prefer to wait to complete the evaluations until after prelim 2, please feel free to do so. But please don't forget!*

---
name: prelim-2

# Prelim 2

Same format as prelim 1 (write answers and code in `.qmd`, submit `.qmd`+`.pdf`)

- **Covers everything since prelim 1** (weeks 7-14)
- *Tentative* plan is to have ~8 questions:
  - ~2 require no coding: "Name X ways to improve this data visualization"
      - Tip: study the prologue sections of slides
  - ~1 is a mix of how to improve a dataviz, and then actually doing it
  - ~5 are coding questions where we specify the goal, and you get there
      - ~3 have a sub-part where you describe an approach w/o writing code
- I will list the number of points per question to help you allocate effort

I pre-tested the prelim and believe it will be challenging but manageable

Questions?

---
class: inverse, center, middle
name: lab

# lab-14


