---
title: "Conclusion"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)
```



class: center, middle

# Conclusion

.class-info[

**Week 15**

AEM 2850: R for Business Analytics<br>
Cornell Dyson<br>
Spring 2022

<!-- Acknowledgements:  -->
<!-- [Andrew Heiss](https://datavizm20.classes.andrewheiss.com) -->
<!-- [Claus Wilke](https://wilkelab.org/SDS375/) -->
<!-- [Grant McDermott](https://github.com/uo-ec607/lectures) -->
<!-- [Jenny Bryan](https://stat545.com/join-cheatsheet.html), -->
<!-- [Allison Horst](https://github.com/allisonhorst/stats-illustrations) -->
<!-- [Ed Rubin](https://github.com/edrubin/EC524W22) -->
]

---

# Announcements

Lab-14 deadline extended to Wednesday

Final project plan feedback on canvas

Final project details, rubric [posted on course site](https://aem2850.toddgerarden.com/assignment/final-project/)

Extra office hours appointments

Questions before we get started?

---

# Plan for today

[Course evaluations](#course-evals)

[Final project guidance](#final-project)

<!-- [Parting thoughts](#parting-thoughts) -->

---
class: inverse, center, middle
name: course-evals

# Course evaluations

---

# Course objectives reminder

1. Develop basic proficiency in `R` programming
2. Understand data structures and manipulation
3. Describe effective techniques for data visualization and communication
4. Construct effective data visualizations
5. Utilize course concepts and tools for business applications

---

# Where we've been (weeks 1-4)

1. **Develop basic proficiency in `R` programming**
2. **Understand data structures and manipulation**
3. Describe effective techniques for data visualization and communication
4. Construct effective data visualizations
5. Utilize course concepts and tools for business applications

---

# Where we've been (weeks 5-10)

1. Develop basic proficiency in `R` programming
2. Understand data structures and manipulation
3. **Describe effective techniques for data visualization and communication**
4. **Construct effective data visualizations**
5. **Utilize course concepts and tools for business applications**

---

# Where we've been (weeks 11-15)

1. **Develop basic proficiency in `R` programming**
2. **Understand data structures and manipulation**
3. **Describe effective techniques for data visualization and communication**
4. **Construct effective data visualizations**
5. **Utilize course concepts and tools for business applications**

---

# Where we're going next (weeks 15+)

Last week we covered **web scraping** by popular demand

This week we'll wrap up the course

**Please feel free to come see me in office hours if you want to discuss topics we didn't have time to cover this semester**

---

# Course evaluations

I take feedback seriously and will use it to improve this course!

Extra useful since this is the first offering of AEM 2850

--

Concrete suggestions are most helpful

--

**I would appreciate your feedback through two channels:**

1. Reflection - Week 15 - Course Feedback Survey
2. University course evaluations

--

Both will be anonymous

---

# University course evaluations

Anonymous: we just get summary reports, after grades are submitted

I will give you time to complete them in class next Tuesday

**I will award a bonus point on Reflection 15 for completing evaluations**

Thank you in advance for your feedback!

--

**I will give you time now to complete evaluations in class**

---
class: inverse, center, middle
name: final-project

# Final project

---

# Key steps and timeline

### ~~Step 1: Choose a group by Friday, April 29~~

### ~~Step 2: Choose data and make a plan by Thursday, May 5~~

### Step 3: Execute your plan

### Step 4: Submit your final project by Thursday, May 19 at 4:30pm

---

# Expectations and grading

I posted more detailed instructions and a grading rubric [on the course site](https://aem2850.toddgerarden.com/assignment/final-project/)

Let's go through them now

--

Any questions?

<!-- --- -->
<!-- class: inverse, center, middle -->
<!-- name: parting-thoughts -->

<!-- # Parting thoughts -->


<!-- GO BACK TO FIRST SLIDE DECK AND COPY IN SOME CONTENT? -->

<!-- GET SOMETHING FROM ANDREW HEISS? -->

<!-- LET THEM OUT EARLY! -->

