---
title: "Conclusion"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)
```


class: center, middle

# Course evaluations

.class-info[

**Week 15**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Fall 2025

]

---

# Course objectives reminder

1. Develop basic proficiency in `R` programming
2. Understand data structures and manipulation
3. Describe effective techniques for data visualization and communication
4. Construct effective data visualizations
5. Utilize course concepts and tools for business applications

With these objectives in mind...

---

# Please take 10 mins to complete course evals

I take feedback seriously and will use it to improve this course!

**I would appreciate your feedback through the *anonymous* university course evaluations**

Concrete suggestions are most helpful

**I will award a bonus point to class participation for completing evaluations**

Thank you in advance for your feedback!
