---
title: "Conclusion"
author: "Todd Gerarden"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    css: ["xaringan-themer.css", "css/tdg-slides.css"]
#    css: ['default', 'metropolis', 'metropolis-fonts']
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
      ratio: "16:9"
      navigation:
        scroll: false
      # beforeInit: "libs/offline-mathjax.js"
editor_options: 
  chunk_output_type: console
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#B31B1B",
                  text_font_size = "1.4rem")
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(warning = FALSE, message = FALSE, 
                      #cache = TRUE,
                      fig.retina = 3, fig.align = "center",
                      fig.width=14, fig.height=7)
```

```{r packages-data, include=FALSE}
library(tidyverse)
```


class: center, middle

# Conclusion

.class-info[

**Week 15**

AEM 2850 / 5850 : R for Business Analytics<br>
Cornell Dyson<br>
Fall 2025

]

---

# Announcements

Plan for this week:
  - Tuesday: slides and a short example
  - Thursday: prelim 2 Q&A, time to complete course evaluations, **homework-14**
    - If you come to class and work through the homework, you will get full credit
    - Due Thursday at 11:59pm so you can focus on studying for prelim 2

--

Plan for next week:
  - **Prelim 2** in class on Tuesday, May 6
  - **Homework 15 - Course Survey** due Monday, May 12 at 11:59pm
    - I will give you time in class on Thursday to complete this

--

Questions before we get started?

---

# Plan for this week

.pull-left[
### Tuesday
  - [Prelim 2 Q&A](#prelim-2)
  - [Complete course evaluations](#course-evals-in-class)
]

.pull-right[
### Thursday
  - [In Class: optional open office hours with TAs](#prelim-2)
  - [Evening: Prelim 2](#prelim-2)
]

---
class: inverse, center, middle
name: course-evals

# Course evaluations

---

# Course objectives reminder

1. Develop basic proficiency in `R` programming
2. Understand data structures and manipulation
3. Describe effective techniques for data visualization and communication
4. Construct effective data visualizations
5. Utilize course concepts and tools for business applications

With these objectives in mind...

---

# Please complete course evaluations

I take feedback seriously and will use it to improve this course!

--

Concrete suggestions are most helpful

--

**I would appreciate your feedback through two *anonymous* channels:**

1. Homework 15 - Course Feedback Survey (on canvas)
2. University course evaluations

--

**I will give you time to complete these in class on Thursday**

--

**I will award a bonus point on Homework 15 for completing evaluations**

--

Thank you in advance for your feedback!


---
class: inverse, center, middle
name: prelim-2

# Prelim 2

---

# Prelim 2

Format: paper exam, closed-book (-notes, -computer, etc.)

It will stress concepts more than syntax (but will test both)

We will have multiple question types, including but not limited to:
1. improve this data visualization
2. multiple choice and short answer questions
3. explain how you would approach a coding task, including key functions (but not full code)
4. explain what code we provide would do
5. write short code snippets

---

# Prelim 2 preparation

We will provide practice questions by Friday, May 2

I have extra office hours by appointment May 1 and May 2

The TAs will have regular open office hours May 2 and May 5

The TAs will host an extra review session on May 5 (see canvas for details)

Questions?

---
class: inverse, center, middle
name: course-evals-in-class

# Course evaluations

---

# Please take 10 mins to complete course evals

I take feedback seriously and will use it to improve this course!

Concrete suggestions are most helpful

**I would appreciate your feedback through two channels:**

1. Homework 15 - Course Feedback Survey (on canvas)
2. University course evaluations

Both will be anonymous

Reminder: **bonus point on Homework 15 for completing university evaluations**

